Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-08 ms.tex
rearranging explanation of two-component SED shape equation
still working on description of two-component model...

% re: following sentence --- in the code nu_0 is actually 2997.92458
% because this is the frequency with respect to which DIRBE color correction
% K_100 (and my color correction as well) is referenced

Following the convention of FDS99, $\nu_0$ is chosen to be 3000 GHz. In 
principle, one could imagine this two MBB model to be specified by seven free 
parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, $\beta_2$, $f_1$, 
and $q_1$/$q_2$ and the normalization of $M_{\nu}$. However, as discussed in 
FDS99, $T_1$=$T_1$($T_2$, $\beta_1$, $\beta_2$, $q_1/q_2$) is fully specified 
by these other parameters under the assumption that the temperature of each 
species is determined by maintaining thermal equilibrium with the same ISRF. 
$T_1$ is always related to $T_2$ via a simple power law, although the prefactor
and exponent depend on the parameters $q_1/q_2$, $\beta_1$ and $\beta_2$. 
$q_1/q_2$ encodes the relative emission/absorption cross-sections of the two 
dust species, while $f_1$ dictates the relative amounts of each species 
present.

>>>>

% re: following paragraph --- in the code nu_0 is actually 2997.92458
% because this is the frequency with respect to which DIRBE color correction
% K_100 (and my color correction as well) is referenced

% not sure if `Planck function' is the correct jargon

Where $B_{\nu}$ is the Planck function, $T_1$ is the `cold' dust temperature, 
$T_2$ is the `hot' dust temperature, and $\beta_1$ and $\beta_2$ are the
emissivity power-law indices of the cold and hot components respectively. 
$q_1/q_2$ encodes the relative emission/absorption cross-sections of the two 
dust species, while $f_1$ dictates the relative amounts of each species 
present. Following the convention of FDS99, $\nu_0$ is chosen to be 3000 GHz.

Mathematically, this two-MBB model requires specification of seven 
parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, $\beta_2$, $f_1$, 
$q_1$/$q_2$ and the normalization of $M_{\nu}$. However, under the 
assumption that the temperature of each species is determined by maintaining 
thermal equilibrium with the same ISRF, $T_1$=$T_1$($T_2$, $\beta_1$, 
$\beta_2$, $q_1/q_2$) is fully determined by these other parameters. $T_1$ is 
always related to $T_2$ via a simple power law, although the prefactor and 
exponent depend on the parameters $q_1/q_2$, $\beta_1$ and $\beta_2$ (see FDS99
Equation 14).
